Efficient Handling of String-Number Conversion

### 2020-03-24 evaluation.tex
Update tables in evaluation

We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{6ad261e24})~\cite{z3}, \textsf{Z3Str3}~(\texttt{6ad261e24})~\cite{zheng2013z3}. For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. 
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

@@

The results of the experiments are summarized in Table~\ref{table:base_benchmark}, Table~\ref{table:str_int_benchmark}, and Table~\ref{table:checkLuhn}. Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae. Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
							& UNSAT    &    288  &   221 &   100 &   111 \\
							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
							& UNSAT    &    319  &   240 &   186 &   192 \\
							& $\times$ &    248  &   154 &   615 &   382 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
							& UNSAT    &    820  &   818 &   808 &   772 \\
							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 \\
							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
\multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

% latest backup of table 2
\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
								& UNSAT    &    720  &   660 &   724  &   644 \\
								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
								& UNSAT    &      0  &     0 &     0  &     0 \\
								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

@@

@@

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}

>>>>

We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. 
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

@@

The results of the experiments are summarized in Table~\ref{table:base_benchmark}, Table~\ref{table:str_int_benchmark}, and Table~\ref{table:checkLuhn}. Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae. Rows with heading \texttt{UNKNOWN}, \texttt{TIMEOUT}, or \texttt{ERROR} indicate the number of instances the solver fails to return an answer. \texttt{INCORRECT} shows the number of cases that a tool gives wrong answer\footnote{A correct answer is decided by mainly CVC4, then the consensus of {\tool} or Z3.}.

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
								& UNSAT    & 16393& 15726& 16115& 15396 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   142&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     1&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
								& UNSAT    &   720&   667&   724&   644 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
								& UNSAT    & 17113& 16393& 16839& 16040 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
								& ERROR    &     0&     0&     0&   373 \\
								& INCORRECT&     1&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
								& UNSAT    & 16393& 15726& 16115& 15396 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   142&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     1&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
								& UNSAT    &   720&   667&   724&   644 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& UNKNOWN  &     0&     9&     0&     0 \\
								& TIMEOUT  &     0&     8&     4&    10 \\
								& ERROR    &     0&     0&     0&     6 \\
								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
								& UNSAT    & 17113& 16393& 16839& 16040 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
								& ERROR    &     0&     0&     0&   373 \\
								& INCORRECT&     1&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

% \begin{table}[h]
% \centering
% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
% \scalebox{0.85}{
% \begin{tabular}{|l r | r r r r |}
% \hline
% \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
% \multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
% 							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
% 							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
% \multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
% 							& UNSAT    &    288  &   221 &   100 &   111 \\
% 							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
% \multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
% 							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
% 							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
% \multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
% 							& UNSAT    &    319  &   240 &   186 &   192 \\
% 							& $\times$ &    248  &   154 &   615 &   382 \\\hline
% \multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
% 							& UNSAT    &    820  &   818 &   808 &   772 \\
% 							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
% \multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
% 							& UNSAT    &   1031  &   936 &  1021 &   958 \\
% 							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
% \multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
% 							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
% 							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
% \end{tabular}}
% \label{table:base_benchmark}
% \end{table}

% \begin{table}[h]
% \centering
% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
% \scalebox{0.8}{
% \begin{tabular}{|l r | r r r r|}
% \hline
% \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
% \multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
% 								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
% 								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
% \multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
% 								& UNSAT    &    720  &   660 &   724  &   644 \\
% 								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
% \multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
% 								& UNSAT    &      0  &     0 &     0  &     0 \\
% 								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
% \multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
% 								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
% 								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
% \end{tabular}}
% \label{table:str_int_benchmark}
% \end{table}

@@

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.89s) & \textbf{SAT}(0.45s) & \textbf{ERROR} \\
3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(1.17s) & \textbf{SAT}(0.10s) & \textbf{ERROR} \\
4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) & \textbf{TIMEOUT}    & \textbf{ERROR} \\
5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(11.27s)& \textbf{TIMEOUT}    & \textbf{ERROR} \\
6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.13s) & \textbf{UNKNOWN} \\
7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.29s) & \textbf{ERROR} \\
9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.48s) & \textbf{TIMEOUT} \\
11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.36s) & \textbf{ERROR} \\
12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.38s) & \textbf{TIMEOUT} \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}

@@

% \begin{table}[h]
% \centering
% \caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
% \scalebox{0.9}{
% \begin{tabular}{| c | c c c c|}
% \hline
% \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
% 2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
% 3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
% 4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
% 5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
% 6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
% 7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
% 8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
% 9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
% 10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
% 11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
% 12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
% \end{tabular}}
% \label{table:checkLuhn}
% \end{table}
